### 2025-04-20 evaluating-prediction-accuracy.qmd
20250419 - fixes

```{r}
player_stats_seasonal_subset_IDs %>% 
  filter(!is.na(gsis_id)) %>% 
  group_by(gsis_id) %>% 
  filter(n() > 1) %>% 
  head()
```

@@

```{r}
#| label: fig-calibrationPlotSeasonalOverall
#| fig-cap: "Calibration Plot for Seasonal Projections. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 8

@@

```{r}
#| label: fig-calibrationPlotSeasonalQBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Quarterbacks. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Quarterbacks. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 8

@@

```{r}
#| label: fig-calibrationPlotSeasonalRBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Running Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Running Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 8

@@

```{r}
#| label: fig-calibrationPlotSeasonalWRs
#| fig-cap: "Calibration Plot for Seasonal Projections of Wide Receivers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Wide Receivers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 8

@@

```{r}
#| label: fig-calibrationPlotSeasonalTEs
#| fig-cap: "Calibration Plot for Seasonal Projections of Tight Ends. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Tight Ends. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 8

@@

```{r}
#| label: fig-calibrationPlotSeasonalKs
#| fig-cap: "Calibration Plot for Seasonal Projections of Kickers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Kickers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 8

@@

```{r}
#| label: fig-calibrationPlotSeasonalDLs
#| fig-cap: "Calibration Plot for Seasonal Projections of Defensive Linemen. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Defensive Linemen. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 8

@@

#### Linebackers {#sec-accuracyProjectionsSeasonalDL}

@@

```{r}
#| label: fig-calibrationPlotSeasonalLBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Linebackers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Linebackers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 8

@@

```{r}
#| label: fig-calibrationPlotSeasonalDBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Defensive Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Defensive Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 8
#| fig-height: 8

>>>>

@@

```{r}
#| label: fig-calibrationPlotSeasonalOverall
#| fig-cap: "Calibration Plot for Seasonal Projections. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 6
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalQBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Quarterbacks. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Quarterbacks. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 6
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalRBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Running Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Running Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 6
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalWRs
#| fig-cap: "Calibration Plot for Seasonal Projections of Wide Receivers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Wide Receivers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 6
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalTEs
#| fig-cap: "Calibration Plot for Seasonal Projections of Tight Ends. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Tight Ends. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 6
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalKs
#| fig-cap: "Calibration Plot for Seasonal Projections of Kickers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Kickers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 6
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalDLs
#| fig-cap: "Calibration Plot for Seasonal Projections of Defensive Linemen. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Defensive Linemen. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 6
#| fig-height: 6

@@

#### Linebackers {#sec-accuracyProjectionsSeasonalLB}

@@

```{r}
#| label: fig-calibrationPlotSeasonalLBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Linebackers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Linebackers. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 6
#| fig-height: 6

@@

```{r}
#| label: fig-calibrationPlotSeasonalDBs
#| fig-cap: "Calibration Plot for Seasonal Projections of Defensive Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-alt: "Calibration Plot for Seasonal Projections of Defensive Backs. The yellow line is the best-fit line based on LOESS. The purple band is the 95% confidence interval of actual fantasy points. The dashed red lines are the 95% prediction interval of actual fantasy points."
#| fig-width: 6
#| fig-height: 6

### 2025-04-20 multiple-regression.qmd
20250418 - fix plot order
20250419 - fixes

@@

abline(
  lm(linearY ~ quadraticX),
  lwd = 2,
  col = "blue")
```

@@

To evaluate homoscedasticity, we can evaluate a residual plot (@fig-residualPlots) and spread-level plot (@fig-spreadLevelPlots) from the `car` package [@Fox2019_packages; @R-car].
In a residual plot, you want a constant spread of residuals versus fitted values—you do not want the residuals to show a fan or cone shape.

>>>>

abline(
  lm(linearY ~ quadraticX),
  lwd = 2,
  col = "blue")

@@

lines(
  quadraticNewData$quadraticY ~ quadraticNewData$quadraticX,
  lwd = 2,
  col = "blue")
```

@@

To evaluate homoscedasticity, we can evaluate a residual plot (@fig-residualPlots) and spread-level plot (@fig-spreadLevelPlot) from the `car` package [@Fox2019_packages; @R-car].
In a residual plot, you want a constant spread of residuals versus fitted values—you do not want the residuals to show a fan or cone shape.
